---
title: "`r params$doc_title`"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    css: style.css
    source_code: https://github.com/bcgov/Industry_Trades_Authority
params:
  doc_title: "Forecasts of Industry Trade Authority new apprenticeship registrations"
---

```{r}
library(flexdashboard)
library(knitr)
library(tidyverse)
library(DT)
library(plotly)
library(here)
library(reactable)
library(viridis)
library(colorspace) # For luminance calculation
theme_set(theme_grey(base_size = 15))
#functions--------------
source(here("R","functions.R"))
#load dataframes-------------------
fcast_tbbl <- read_rds(here("processed_data","fcast_tbbl.RDS"))
fcast_long <- read_rds(here("processed_data","fcast_long.RDS"))

max_year <- fcast_tbbl|>
  filter(!is.na(`New Registrations`))|>
  slice_max(year, with_ties = FALSE)|>
  pull(year)|>
  as.numeric()

page_titles <- c("Title Page",#replace with your page titles
                 "Methodology",
                 "All groups, British Columbia",
                 "All groups, by region",
                 "Skilled Trades Certification (STC), BC",
                 "Skilled Trades Certification (STC), by region",
                 "British Columbia, by group",
                 "Lower Mainland Southwest",
                 "Vancouver Island and Coast",
                 "South East",
                 "North",
                 "Data table"
                 )

```

# `r page_titles[1]` {data-navmenu="Table of Contents"}

## Row {.background-banner}

<br><br><br><br><br><br><br><br>

<h1 class="center">

`r params$doc_title`.

</h1>

# `r page_titles[2]` {data-navmenu="Table of Contents"}

## Row {data-height="800"}

### Data  

```{r}
# for methodology explanation.

rt <- fcast_tbbl%>%
  filter(drname=="British Columbia",
         group=="All groups",
         year<=max_year)%>%
  select(-drname, -group, -scaled_up)|>
  relocate(prop_mean, .after = everything())|>
  mutate(employment=round(employment))

htmltools::div(
  style = "flex-grow: 1; overflow-y: auto;",
  color_duplicate_cells(rt)
)

```

## Row {data-height="400"}

### Methodology

*  For example, consider the data above (all trades groups for British Columbia).
*  **New Registrations ** is the aggregate value of new registrations for a given **year**, **drname** and **group**. 
*  Note that for the `r max_year` new registrations, the value you see is 12 times the year-to-date monthly average.
*   **employment** is from the LFS up to `r max_year-1`, and from the LMO forecast for `r max_year` onwards.
*   **prop_year** : we use the historic relationship between new registrations and employment in that **year**, and apply it to all the years of LFS (backcasts) and LMO employment (forecasts).
*   **prop_mean**: same as above, but proportion is the average across all years between 2016 and `r max_year-1`.
*   The coloured cells indicate matching values of new registrations and backcasts: i.e. if you apply the 2016 proportion to 2016 employment, you recover (perfectly) the observed number of new registrations.

# `r page_titles[3]` {data-navmenu="Table of Contents"}

## Column

### New registrations for `r page_titles[3]` (black) and fore/back-casts (red). 

```{r fig.width=16, fig.height=8}
total <- fcast_long%>%
  filter(drname=="British Columbia",
         group=="All groups")
plt <- plot_casts(total)

plotly::ggplotly(plt, tooltip = "text")
```

# `r page_titles[4]` {data-navmenu="Table of Contents"}

## Column

### New registrations for `r page_titles[4]` (black) and fore/back-casts (red). 

```{r fig.width=16, fig.height=8}
by_region <- fcast_long%>%
  filter(group=="All groups",
         drname!="British Columbia",
         drname!="NULL")

plt <- plot_casts(by_region)+
    facet_wrap(~fct_reorder(drname, value, .desc = TRUE), scales = "free_y")

plotly::ggplotly(plt, tooltip = "text")
```

# `r page_titles[5]` {data-navmenu="Table of Contents"}

## Column

### New registrations for `r page_titles[5]` (black) and fore/back-casts (red). 

```{r fig.width=16, fig.height=8}
by_region <- fcast_long%>%
  filter(group=="STC Trades",
         drname=="British Columbia")
plt <- plot_casts(by_region)+
    facet_wrap(~fct_reorder(drname, value, .desc = TRUE), scales = "free_y")

plotly::ggplotly(plt, tooltip = "text")
```

# `r page_titles[6]` {data-navmenu="Table of Contents"}

## Column

### New registrations for `r page_titles[6]` (black) and fore/back-casts (red). 

```{r fig.width=16, fig.height=8}
by_region <- fcast_long%>%
  filter(group=="STC Trades",
         drname!="British Columbia",
         drname!="NULL")
plt <- plot_casts(by_region)+
    facet_wrap(~fct_reorder(drname, value, .desc = TRUE), scales = "free_y")

plotly::ggplotly(plt, tooltip = "text")
```


# `r page_titles[7]` {data-navmenu="Table of Contents"}

## Column

### New registrations for `r page_titles[7]` (black) and fore/back-casts (red). 

```{r fig.width=16, fig.height=8}
bc_by_group <- fcast_long%>%
  filter(group!="All groups",
         group!="STC Trades",
         drname=="British Columbia")
plt <- plot_casts(bc_by_group)+
    facet_wrap(~fct_reorder(group, value, .desc = TRUE), scales = "free")

plotly::ggplotly(plt, tooltip = "text")
```

# `r page_titles[8]` {data-navmenu="Table of Contents"}

## Column

### New registrations for `r page_titles[8]` (black) and fore/back-casts (red). 

```{r fig.width=16, fig.height=8}
lml_by_group <- fcast_long%>%
  filter(group!="All groups",
         group!="STC Trades",
         drname=="Mainland South West")
plt <- plot_casts(lml_by_group)+
    facet_wrap(~fct_reorder(group, value, .desc = TRUE), scales = "free_y")

plotly::ggplotly(plt, tooltip = "text")
```

# `r page_titles[9]` {data-navmenu="Table of Contents"}

## Column

### New registrations for `r page_titles[9]` (black) and fore/back-casts (red). 

```{r fig.width=16, fig.height=8}
island_by_group <- fcast_long%>%
  filter(group!="All groups",
         group!="STC Trades",
         drname=="Vancouver Island Coast")
plt <-   plot_casts(island_by_group)+
    facet_wrap(~fct_reorder(group, value, .desc = TRUE), scales = "free_y")

plotly::ggplotly(plt, tooltip = "text")
```

# `r page_titles[10]` {data-navmenu="Table of Contents"}

## Column

### New registrations for `r page_titles[10]` (black) and fore/back-casts (red). 

```{r fig.width=16, fig.height=8}
south_by_group <- fcast_long%>%
  filter(group!="All groups",
         group!="STC Trades",
         drname=="Southeast")
plt <-   plot_casts(south_by_group)+
    facet_wrap(~fct_reorder(group, value, .desc = TRUE), scales = "free_y")

plotly::ggplotly(plt, tooltip = "text")
```

# `r page_titles[11]` {data-navmenu="Table of Contents"}

## Column

### New registrations for `r page_titles[11]` (black) and fore/back-casts (red). 

```{r fig.width=16, fig.height=8}
north_by_group <- fcast_long%>%
  filter(group!="All groups",
         group!="STC Trades",
         drname=="North")
plt <-   plot_casts(north_by_group)+
    facet_wrap(~fct_reorder(group, value, .desc = TRUE), scales = "free_y")

plotly::ggplotly(plt, tooltip = "text")
```

# `r page_titles[12]` {data-navmenu="Table of Contents"}

## Column

### Click &darr; to download data

```{r}
fcast_tbbl %>%
  DT::datatable(
    rownames = FALSE,
    escape = FALSE,
    extensions = c('Buttons', 'FixedColumns'),
    class = 'cell-border stripe',
    options = list(
    pageLength = 100,
    dom = 'Bfrtip',
    scrollX = TRUE,
    buttons = c('csv', 'excel')))
```
