---
title: \textcolor{black}{New Apprenticeship Registrations and Apprenticeship Certifications}
subtitle: \textcolor{black}{`r paste("for",format(readRDS(here::here("processed_data","max_date.rds")), format="%B %Y"))`}
author: "Labour Market Information Office"
institute: "Contact: Richard.Martin@gov.bc.ca"
date: "`r lubridate::today()`"
header-includes: 
- \usepackage{booktabs}
- \usepackage{colortbl}
- \usepackage{makecell}
- \usepackage{xcolor}
- \usepackage{longtable}
- \definecolor{bcblue}{HTML}{1f4181}
- \definecolor{bcyellow}{HTML}{ffba2a}
- \setbeamercolor*{palette primary}{use=structure,fg=white,bg=bcblue}
- \setbeamercolor*{palette quaternary}{use=structure,fg=white,bg=bcyellow}
- \setbeamercolor{title}{fg=bcblue}
- \setbeamercolor{frametitle}{fg=bcblue}
- \useoutertheme{split}
output:
  beamer_presentation:
    theme: "Boadilla"
    fonttheme: "structurebold"
urlcolor: blue
linkcolor: blue
classoption: "aspectratio=169"
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE)
library(tidyverse)
library(fpp3)
library(here)
library(janitor)
library(readxl)
library(cansim)
library(kableExtra)
library(ggfortify)
library(grid)
library(tidyquant)
add_months <- 1 # once we are in the last add_months of the year we report the forecast for the following year (rather than forecasting the current year.)
source(here("R","functions.R"))

theme_set(theme_grey(base_size = 15))
mapping <- read_csv(here("current_data","mapping","mapping.csv"))
new_reg <- read_clean_join("New")

by_year_and_age <- new_reg%>%
  group_by(year, age_group_registration_start)%>%
  summarize(count=sum(count, na.rm=TRUE))%>%
  filter(!stringr::str_detect(age_group_registration_start, "="),
         age_group_registration_start!="NULL")

pop <- read_rds(here::here("current_data","lmo","pop.rds"))

prop_reg <- full_join(by_year_and_age, pop, by=c("year"="year","age_group_registration_start"="age_group"))%>%
  mutate(prop=count/value)

new_reg_total <- new_reg%>%
  just_aggregate()%>%
  fix_dates()
max_date <- yearmonth(max(new_reg_total$date))
max_year <- year(max_date)
stc_new_reg <- new_reg%>%
  filter_and_aggregate(stc, "equal", "STC Trades")%>%
  fix_dates()
cofq <- read_clean_join("CofQ")
cofq_total <- cofq%>%
  just_aggregate(program_type)%>%
  fix_dates()
cofq_app <- cofq_total%>%
  filter(program_type=="Apprenticeship")
cofq_chal <- cofq_total%>%
  filter(program_type=="Challenge")

bc_fcast <- read_rds(here("processed_data","fcast_long.RDS"))|>
  filter(drname=="British Columbia")

forecast_growth <- bc_fcast%>%
  filter(group=="All groups", 
         name=="prop_mean"
         )%>%
  fcast_growth(year(today()+month(add_months)), year(today()+month(add_months)+year(1)))
```

## Highlights

- Comparisons to same month last year:
  - New apprenticeship registrations in `r max_date` were `r describe_change(get_growth(new_reg_total, years, 1))`.
  - Registrations in the Skilled Trades Certification (STC) trades occupations in `r max_date` were `r describe_change(get_growth(stc_new_reg, years, 1))`.
  - Certificates of Qualification issued in `r max_date` were `r describe_change(get_growth(cofq_app, years, 1))` for Apprentices.
  - Certificates of Qualification issued in `r max_date` were `r describe_change(get_growth(cofq_chal, years, 1))` for Trade Qualifiers.

- Forecast for next year:
  - Relative to last year, new apprenticeship registrations in `r year(today()+months(add_months))` are forecast to be `r describe_change(forecast_growth)`.

## New Apprentice Registrations: [Total*](#Total)
::: columns 
:::: {.column width=.05}
::::
:::: {.column width=.6}
### \textcolor{bcblue}{Put some commentary here} 
```{r, echo=FALSE, fig.show='hold', fig.height=6}
decomp_plot(new_reg_total)
```
::::
::::  {.column width=.35}
- Compared to the same month last year, New apprenticeship registrations were `r describe_change(get_growth(new_reg_total, years, 1))`.
- Compared to last month, New apprenticeship registrations were `r describe_change(get_growth(new_reg_total, months, 1))`.
::::
:::

## New Apprentice Registrations: [Skilled Trades Certification*](#STC) 
::: columns 
:::: {.column width=.05}
::::
:::: {.column width=.6}
### \textcolor{bcblue}{Put some commentary here} 
```{r, echo=FALSE, fig.show='hold', fig.height=6}
  decomp_plot(stc_new_reg)
```
::::
::::  {.column width=.35}
- Compared to the same month last year, STC new registrations were `r describe_change(get_growth(stc_new_reg, years, 1))`.
- Compared to last month, STC new registrations were `r describe_change(get_growth(stc_new_reg, months, 1))`.
::::
:::

## Certificate of Qualification: Total
::: columns 
:::: {.column width=.05}
::::
:::: {.column width=.6}
### \textcolor{bcblue}{Put some commentary here} 
```{r, echo=FALSE, fig.show='hold', fig.height=6}
cofq_agg <- cofq_total%>%
  group_by(date)%>%
  summarize(count=sum(count))
decomp_plot(cofq_agg)
```
::::
::::  {.column width=.35}
- Compared to the same month last year, Certificates of Qualification were `r describe_change(get_growth(cofq_agg, years, 1))`.
- Compared to last month,  Certificates of Qualification were `r describe_change(get_growth(cofq_agg, months, 1))`.
::::
:::

## Certificate of Qualification: [Apprenticeship route*](#A1)
::: columns 
:::: {.column width=.05}
::::
:::: {.column width=.6}
### \textcolor{bcblue}{Put some commentary here} 
```{r, echo=FALSE, fig.show='hold', fig.height=6}
decomp_plot(cofq_app)
```
::::
::::  {.column width=.35}
- Compared to the same month last year, Certificates of Qualification (apprentice route) were `r describe_change(get_growth(cofq_app, years, 1))`.
- Compared to last month,  Certificates of Qualification (apprentice route) were `r describe_change(get_growth(cofq_app, months, 1))`.
::::
:::

## Certificate of Qualification: [Challenge route*](#A1)
::: columns 
:::: {.column width=.05}
::::
:::: {.column width=.6}
### \textcolor{bcblue}{Put some commentary here} 
```{r, echo=FALSE, fig.show='hold', fig.height=6}
decomp_plot(cofq_chal)
```
::::
::::  {.column width=.35}
- Compared to the same month last year, Certificates of Qualification (challenge route) were `r describe_change(get_growth(cofq_chal, years, 1))`.
- Compared to last month, Certificates of Qualification (challenge route) were `r describe_change(get_growth(cofq_chal, months, 1))`.
::::
:::

## New Apprenticeship Registrations: [Total*](#Total)
::: columns 
:::: {.column width=.05}
::::
:::: {.column width=.6}
### \textcolor{bcblue}{Demand driven forecast: proportion of employment} 
```{r, echo=FALSE, fig.show='hold', fig.height=6}
bc_fcast|>
  filter(group=="All groups")|>
  plot_casts()

get_fcast <- function(grp, yr, nm){
  bc_fcast%>%
    filter(year==yr, 
           group==grp,
           name==nm)%>%
    pull(value)
}

get_cagr <- function(grp){
  current_year <- year(today())
  future_year <- max(bc_fcast$year)
  current_forecast <- get_fcast(grp, current_year, "prop_mean")
  future_forecast <- get_fcast(grp, future_year, "prop_mean")
  scales::percent((future_forecast/current_forecast)^(1/(future_year-current_year))-1, accuracy = .1)  
}

```
::::
::::  {.column width=.35}
- Black line is annual registrations `r paste(year(min(new_reg_total$date)), year(max(new_reg_total$date))-1, sep="-")`, and scaled up monthly registrations for `r year(max(new_reg_total$date))`.
- Light red lines based on individual year proportions.
- Dark red line based on a multi-year proportion: $\scriptscriptstyle \frac{\sum_{2016}^{2024}registrations}{\sum_{2016}^{2024}employment}$. 
- In `r year(today())` new registrations are forecast to be `r get_fcast("All groups", year(today()), "prop_mean")%>%scales::comma()`.
- The growth rate in new registrations from `r year(today())` to `r max(bc_fcast$year)` is forecast to be `r get_cagr("All groups")`
::::
:::


## New Apprenticeship Registrations: [Skilled Trades Certification*](#STC)
::: columns 
:::: {.column width=.05}
::::
:::: {.column width=.6}
### \textcolor{bcblue}{Demand driven forecast: proportion of employment} 
```{r, echo=FALSE, fig.show='hold', fig.height=6}
 bc_fcast|>
  filter(group=="STC Trades")|>
  plot_casts()
```
::::
::::  {.column width=.35}
- Black line is annual registrations `r paste(year(min(new_reg_total$date)), year(max(new_reg_total$date))-1, sep="-")`, and scaled up monthly registrations for `r year(max(new_reg_total$date))`.
- Light red lines based on individual year proportions.
- Dark red line based on a multi-year proportion: $\scriptscriptstyle \frac{\sum_{2016}^{2024}registrations}{\sum_{2016}^{2024}employment}$. 
- In `r year(today())` new registrations are forecast to be `r get_fcast("STC Trades", year(today()), "prop_mean")%>%scales::comma()`.
- The growth rate in new registrations from `r year(today())` to `r max(bc_fcast$year)` is forecast to be `r get_cagr("STC Trades")`
::::
:::

## New Apprenticeship Registrations: [Structural Building Trades*](#SBT)
::: columns 
:::: {.column width=.05}
::::
:::: {.column width=.6}
### \textcolor{bcblue}{Demand driven forecast: proportion of employment} 
```{r, echo=FALSE, fig.show='hold', fig.height=6}
 bc_fcast|>
  filter(group=="Structural Building Trades")|>
  plot_casts()
```
::::
::::  {.column width=.35}
- Black line is annual registrations `r paste(year(min(new_reg_total$date)), year(max(new_reg_total$date))-1, sep="-")`, and scaled up monthly registrations for `r year(max(new_reg_total$date))`.
- Light red lines based on individual year proportions.
- Dark red line based on a multi-year proportion: $\scriptscriptstyle \frac{\sum_{2016}^{2024}registrations}{\sum_{2016}^{2024}employment}$. 
- In `r year(today())` new registrations are forecast to be `r get_fcast("Structural Building Trades", year(today()),"prop_mean")%>%scales::comma()`.
- The growth rate in new registrations from `r year(today())` to `r max(bc_fcast$year)` is forecast to be `r get_cagr("Structural Building Trades")`
::::
:::


## Population Comparison
::: columns 
:::: {.column width=.05}
::::
:::: {.column width=.6}
### \textcolor{bcblue}{Ratio of New Registrations to Population} 
```{r, echo=FALSE, fig.show='hold', fig.height=6}
  ggplot(prop_reg, aes(age_group_registration_start, prop, fill=as.factor(year)))+
  geom_col(position = "dodge")+
  scale_fill_viridis_d()+
  labs(x="Age Group", y="",fill="", caption="Population data from Statistics Canada table 17-10-0005-01")+
  scale_y_continuous(labels=scales::percent)
```
::::
::::  {.column width=.35}
- People under 30 are those most likely to register for an apprenticeship.
- People of all ages were less likely to register for an apprenticeship in 2020. 
- For all age groups the proportion of new registrations is no lower than pre-COVID. 
::::
:::

## Appendix 1 {#A1}

- Source Code: [Github](https://github.com/bcgov/Industry_Trades_Authority)
- New registration forecasts are the product of the historic ratio between new registrations and employment and the forecast of trades employment from the last published edition of the BC Labour Market Outlook (LMO). 
- The current year forecast (`r year(max(new_reg_total$date))`) is a weighted average of new registrations thus far and the demand driven forecast described above.
- Historical data on New Apprenticeship Registrations and Certificates of Qualification was provided by SkilledTradesBC.
- Certificates of Qualification can be earned through two pathways: The completion of an apprenticeship program (Apprentice route, called “Apprentices”) or by challenging the certification exam (Challenge route, called “Trade Qualifiers”)

## Appendix 2: STC trades {#STC}

- These are the first 10 trades to undergo mandatory certification.

```{r}
stc <- mapping%>%
  filter(stc=="STC Trades")%>%
  select(noc_code, description)
colnames(stc) <- c("NOC Code", "Description")
kable(stc, booktabs = T)%>%
  kable_styling(latex_options = "striped")
```

## Appendix 3: Functional Trade Groups: {#FTG}

```{r}
ftg <- new_reg%>%
  select(functional_trades_group)%>%
  distinct()%>%
  na.omit()
colnames(ftg) <- make_title(colnames(ftg))
kable(ftg, booktabs = T)%>%
  kable_styling(latex_options = "striped")
```

## Appendix 4: Structural Building Trades: {#SBT}

```{r}
sbt <- new_reg%>%
  filter(functional_trades_group=="Structural Building Trades")%>%
  select(noc_code, description)%>%
  distinct()%>%
  na.omit()
colnames(sbt) <- c("NOC Code", "Description")
kable(sbt, booktabs = T)%>%
  kable_styling(latex_options = "striped", font_size = 7)
```

## Appendix 5: All trade occupations {#Total}

```{r, message=FALSE}
all_trades <- new_reg%>%
  filter(trades=="Trades")%>%
  select(noc_code, description)%>%
  distinct()

first <- head(all_trades, n=ceiling(nrow(all_trades)/2))
second <- tail(all_trades, n=ceiling(nrow(all_trades)/2))
all <- bind_cols(first, second)

kable(all, 
      booktabs = T,
      col.names = c("NOC Code",
                           "Description",
                           "NOC Code",
                           "Description"))%>%
  kable_styling(latex_options = "striped", font_size = 5)
```




